A Real-Time Sonar Simulator for Automatic Target Recognition

### 2015-10-29 Simulator/article.tex
la2pdf commit - 2015:10:29	11:48:08	(Thu29.Oct)

One of the major shortcomings of autonomous underwater vehicles (AUVs) is their lack of intelligence. When an AUV equipped with a sonar encounter an interesting object, it would be very beneficial if adapted its behavior to examine the object further. This is challenging as what we deem as interesting is often something that stand out form the background, i.e. it relies on previous knowledge. It would also need to process this information is near real-time to act in an efficient manner.

>>>>

\IEEEPARstart{O}{ne} of the greatest visions of science is to create intelligent machines. This is This is especially true for devices designed to sense and act without aid, such as autonomous underwater vehicles (AUVs). The potential here seems only limited by our imagination. When an AUV equipped with a sonar encounter an interesting object, it would be very beneficial if adapted its behavior to examine the object further. This is challenging as what we deem as interesting is often something that stand out form the background, i.e. it relies on previous knowledge. It would also need to process this information is near real-time to act in an efficient manner.
